### 2018-09-13 thesis_report/theory.tex
Add makefile to compile latex on io. Add snippets.

\chapter{Theory}

%%--------------------------------------------------------------------------
%% Topology in solid state physics
%%-----------------------includeonly---------------------------------------------------
\section{Topology in solid state physics}
The Wikipedia definition of mathematical topology is as follows: \quote{Topology can be formally defined as "the study of qualitative properties of certain objects (called topological spaces) that are invariant under a certain kind of transformation}\cite{wiki:topology}\\
Hello

>>>>

% Momentum operators
\newcommand{\kx}{k_x}
\newcommand{\ky}{k_y}

% Pauli matrices
\newcommand{\sigx}{\sigma_x}
\newcommand{\sigy}{\sigma_y}
\newcommand{\sigz}{\sigma_z}
\newcommand{\sigi}{\sigma_0}
\newcommand{\taux}{\tau_x}
\newcommand{\tauy}{\tau_y}
\newcommand{\tauz}{\tau_z}
\newcommand{\taui}{\tau_0}
\chapter{Theory}

%%██████████████████████████████████████████████████████████████████████████
%%██ General Physics
%%██████████████████████████████████████████████████████████████████████████
\section{General Physics}
%%--------------------------------------------------------------------------
%%  Spin-orbit coupling
    \subsection{Spin-orbit coupling}
    Rashba spin orbit coupling:
    \begin{equation}
    	H_\text{Rashba} = \alpha (\ky \sigx - \kx \sigy) 
    \end{equation}

%%--------------------------------------------------------------------------
%%  Supercurrent
    \subsection{Supercurrent}
    As the field we are describing is 
%%▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓

%%██████████████████████████████████████████████████████████████████████████
%%██ Tight binding
%%██████████████████████████████████████████████████████████████████████████
\section{Tight binding}

%%▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓

%%██████████████████████████████████████████████████████████████████████████
%%██ Topology in solid state physics
%%██████████████████████████████████████████████████████████████████████████
\section{Topology in solid state physics}     The Wikipedia definition of
mathematical topology is as follows: \quote{Topology can be formally defined as
"the study of qualitative properties of certain objects (called topological
spaces) that are invariant under a certain kind of
transformation}\cite{wiki:topology}\\

%%-------------------------------------------------------------------------- 
%% Symmetries     
\subsection{Symmetries}

%%▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓
